Computable Poincar\'e--Friedrichs constants for the $L^{p}$ de~Rham complex over convex domains and domains with shellable triangulations

### 2025-01-15 main.tex
clean up

\begin{remark}\label{remark:fullrecursivesum}
    \color{red}
    We briefly outline how  to obtain an estimate for the Poincar\'e--Friedrichs constant from the recursive estimate in Theorem~\ref{theorem:poincarefriedrichsestimate:grad}.
    The potential $w$ for the gradient $\nabla u$ satisfies 
    \begin{align*}
        \| w \|_{L^{p}(T_{0})} \leq A_{0} \| \nabla u \|_{L^{p}(T_{0})},
        \qquad 
        % \| w \|_{L^{p}(T_{m})} \leq A_{m} \| \nabla u \|_{L^{p}(T_{m} \cup T_{m-1})}                             + B_{m} \| w \|_{L^{p}(T_{m-1})},
        \| w \|_{L^{p}(T_{m})} \leq A_{m} \| \nabla u \|_{L^{p}(T_{m})} + A'_{m} \| \nabla u \|_{L^{p}(T_{m-1})} + B_{m} \| w \|_{L^{p}(T_{m-1})},
    \end{align*}
    where $A_{m}, A'_{m}, B_{m} \geq 0$ are numbers and $T_{0}, T_{1}, \dots, T_{m-1}, T_{m}$ is a face path.
    Unwrapping the recursion for the norm over the $m$-th simplex, we get a total expression of the form 
    \begin{align}\label{math:fullrecursivesum}
        \| w \|_{L^{p}(T_{m})} 
        &
        \leq 
        \sum_{\ell=0}^{m}   \left( B_{m} \cdots B_{\ell+1} \right) A_{\ell} \| \nabla u \|_{L^{p}(T_{\ell})}
        +
        \sum_{\ell=0}^{m-1} \left( B_{m} \cdots B_{\ell+2} \right) A'_{\ell+1} \| \nabla u \|_{L^{p}(T_{\ell})}
        =:
        \sum_{\ell=0}^{M} C_{m,\ell} \| \nabla u \|_{L^{p}(T_{\ell})}
        .
    \end{align}
    Here, $C_{m,\ell}$ is the coefficient of $\| \nabla u \|_{L^{p}(T_{\ell})}$, possibly zero, as it appears in the unwrapped recursive estimate of $\| w \|_{L^{p}(T_{m})}$. 
    The global Poincar\'e--Friedrichs inequality follows via H\"older's inequality:
    \begin{align*}
        \| w \|_{L^{p}(\Omega)}^{p}
        &
        \leq 
        \sum_{m=0}^{M}
        \| w \|_{L^{p}(T_{m})}^{p}
        % \\&
        \leq 
        \sum_{m=0}^{M}
        \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac p q}
        \sum_{\ell=0}^{M} 
        \| \nabla u \|_{L^{p}(T_{\ell})}^{p} 
        \leq 
        \left(
            \sum_{m=0}^{M}
            \left( \sum_{\ell=0}^{M} C_{m,\ell}^{q} \right)^{\frac p q}
        \right)
        \| \nabla u \|_{L^{p}(\Omega)}^{p} 
        ,
    \end{align*}
    where $q \in [1,\infty]$ satisfies $1 = 1/p + 1/q$ and with obvious modifications if $p=1$ or $p=\infty$. 
    In other words, the Poincar\'e--Friedrichs inequality is estimated by first taking the $q$-norm of the coefficients in the full sum~\eqref{math:fullrecursivesum} and then taking $p$-norm of these intermediate sums.
    Alternatively, when $L$ denotes the longest path, then a different application of H\"older's inequality shows:
    % \begin{align*}
        % \| w \|_{L^{p}(\Omega)}^{p}
        % &
        % \leq 
        % \sum_{m=0}^{M}
        % \| w \|_{L^{p}(T_{m})}^{p}
        % \\&
        % \leq 
        % \sum_{m=0}^{M}
        % L^{\frac p q}
        % \sum_{\ell=0}^{M} C_{m,\ell}^{p} \| \nabla u \|_{L^{p}(T_{\ell})}^{p} 
        % \leq 
        % L^{\frac p q}
        % \sum_{m=0}^{M} 
        % \max_{ 0 \leq \ell \leq M }
        % C_{m,\ell}^{p} 
        % \cdot 
        % \| \nabla u \|_{L^{p}(\Omega)}^{p} 
        % ,
    % \end{align*}

    \color{green}Hence, 
    \begin{align}
        \| w \|_{L^{p}(\Omega)}^{p}
        &
        \leq 
        \sum_{m=0}^{M}
        \| w \|_{L^{p}(T_{m})}^{p}
        \\&
        \leq 
        \sum_{m=0}^{M}
        \sum_{\ell=0}^{M} 
        \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac p q}
        \delta_{m,\ell} \| \nabla u \|_{L^{p}(T_{\ell})}^{p} 
        \\&
        \leq 
        \max_{0 \leq \ell \leq M} \left(
            \sum_{m=0}^{M}
            \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac p q}
            \delta_{m,\ell} 
        \right)
        \cdot 
        \| \nabla u \|_{L^{p}(\Omega)}^{p} 
        \\&
        \leq 
        \left(
            \sum_{m=0}^{M}
            \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac p q}
        \right)
        \cdot 
        \| \nabla u \|_{L^{p}(\Omega)}^{p} 
        .
    \end{align}
    Now, if $q \leq p$, that is, $2 \leq p$, then 
    \begin{align}
        \left(
            \sum_{m=0}^{M}
            \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac p q}
        \right)^{\frac 1 p}
        \leq 
        \left(
            \sum_{\ell'=0}^{M}
            \left( \sum_{m=0}^{M} C_{m,\ell'}^{p} \right)^{\frac q p}
        \right)^{\frac 1 q}
        .
    \end{align}
    Instead, if $p \leq q$, that is, $p \leq 2$, then 
    \begin{align}
        \left(
            \sum_{m=0}^{M}
            \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac p q}
        \right)^{\frac 1 p}
        \leq 
        \sum_{m=0}^{M}
        \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac 1 q}
        \leq 
        \sum_{m=0}^{M}
        \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{p} \right)^{\frac 1 p}
        .
    \end{align}
    So in any case, it is better than using the following Minkowski's inequality: 
    \begin{align}
        \| w \|_{L^{p}(\Omega)}
        &
        \leq 
        \left( \sum_{m=0}^{M} \left( \sum_{\ell=0}^{M} C_{m,\ell} \| \nabla u \|_{L^{p}(T_{\ell})} \right)^{p} \right)^{\frac 1 p}
        \\&
        \leq 
        \sum_{\ell=0}^{M}
        \left( \sum_{m=0}^{M} C_{m,\ell}^{p} \| \nabla u \|_{L^{p}(T_{\ell})}^{p} \right)^{\frac 1 p}
        \leq 
        \sum_{\ell=0}^{M}
        \left( \sum_{m=0}^{M} C_{m,\ell}^{p} \right)^{\frac 1 p}
        \| \nabla u \|_{L^{p}(\Omega)}
        .
    \end{align}
\end{remark}

@@

We analyze the Bogovski\u{\i} potential operator by similar means. 
Suppose that $u \in L^{\infty}\Alt^{\mia}(\bbR^{n})$ with $\supp u \subseteq \overline\Omega$ and that $x \in \bbR^{n}$.
First, if $x \notin \Omega$, then the convexity of $\Omega$ implies that $y + t( x - y ) \notin \Omega$ for all $t > 1$. Hence, $\calG_{\mia}(x,y) = 0$ and therefore $\Bogov_{\mia} u(x) = 0$ in that case.
Consider now the case $x \in \overline\Omega$. 
We estimate $\Bogov_{\mia} u(x)$ pointwise by 
\begin{align*}
    \left| \Bogov_{\mia} u(x) \right|
    &=
    \left| 
        \int_{\Omega} \calG_{\mia}(x,y) \,(x-y)\lrcorner u(y)\,dy
    \right| 
    \\&\leq 
    \int_{\Omega} \vol(\Omega)^{-1} \sum_{\jeza=0}^{\mia-1}\tbinom{\mia-1}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} |x-y|^{\jeza+1-n} |u(y)| \,dy
    \\&\leq 
    \int_{\bbR^{n}} \vol(\Omega)^{-1} \sum_{\jeza=0}^{\mia-1}\tbinom{\mia-1}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} \chi_{B_{\diam(\Omega)}(0)}(x-y) |x-y|^{\jeza+1-n} |u(y)| \,dy
    .
\end{align*}
Using once more the radial integrals discussed above, we compute 
% We recall the radial integrals 
% \begin{align*}
%     \int_{B_{\diam(\Omega)}(0)} |z|^{\jeza+1-n} dz
%     =
%     \vol_{n-1}(S_1) \int_{0}^{\diam(\Omega)} r^{\jeza+1-n} r^{n-1} dr
%     =
%     \vol_{n-1}(S_1) \int_{0}^{\diam(\Omega)} r^{\jeza} dr
%     =
%     \vol_{n-1}(S_1) \frac{\diam(\Omega)^{\jeza+1}}{\jeza+1}
%     .
% \end{align*}
% We compute 
\begin{align*}
    &
    \int_{\bbR^{n}} \sum_{\jeza=0}^{\mia-1} \tbinom{\mia-1}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} \chi_{B_{\diam(\Omega)}(0)}(z) |z|^{\jeza+1-n} \,dz
    \\&
    =
    \sum_{\jeza=0}^{\mia-1} \tbinom{\mia-1}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} \int_{B_{\diam(\Omega)}(0)} |z|^{\jeza+1-n} \,dz
    \\&
    =
    \vol_{n-1}(S_1) \sum_{\jeza=0}^{\mia-1} \tbinom{\mia-1}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} \frac{\diam(\Omega)^{\jeza+1}}{\jeza+1}
    %\\&
    =
    \vol_{n-1}(S_1) \diam(\Omega)^{n+1} \underbrace{ \sum_{\jeza=0}^{\mia-1} \frac{ \tbinom{\mia-1}{\jeza} }{ (n-\jeza)(\jeza+1) } }_{ =: C_{\Bogov}(n,\mia) \leq 2^{\mia-1}}
    .
\end{align*}
% Here, $C_{\Bogov}(n,\mia)$ is a numerical constant that depends only on $n$ and $\mia$ and which is bounded by $2^{\mia-1}$. 
Here we introduce the numerical constant 
\begin{gather}\label{equation:A_Bogov}
    C_{\Bogov}(n,\mia) := \sum_{\jeza=0}^{\mia-1} \frac{ \tbinom{\mia-1}{\jeza} }{ (n-\jeza)(\jeza+1) }, 
\end{gather}
which depends only on $n$ and $\mia$ and which is bounded by $2^{\mia-1}$. 
Similar as above,
the integral $\Bogov_{\mia} u(x)$ is absolutely convergent for any choice of $x \in \bbR^{n}$
and its magnitude is pointwise dominated by the convolution of $|u|$ against an integrable function.
Young's convolution inequality now implies: 
\begin{align*}
    \| \Bogov_{\mia} u \|_{L^{p}(\Omega)}
    &
    \leq 
    \vol_{n-1}(S_1) C_{\Bogov}(n,\mia) \frac{ \diam(\Omega)^{n} }{\vol(\Omega)} 
    \diam(\Omega)
    \| u \|_{L^{p}(\Omega)}
    \\&
    \leq 
    n C_{\Bogov}(n,\mia) \frac{ \vol_{}(B_{\diam(\Omega)}(0)) }{\vol(\Omega)} 
    \diam(\Omega)
    \| u \|_{L^{p}(\Omega)}
    .
\end{align*}
We have assumed so far that $u$ is essentially bounded.
Since that space is dense in the Lebesgue spaces, a density argument yields: 
for any $1 \leq p \leq \infty$ we have a bounded linear operator 
\begin{gather*}
    \Bogov_{\mia} : L^{p}\Alt^{\mia}(\Omega) \rightarrow L^{p}\Alt^{\mia-1}(\bbR^n).
\end{gather*}
% Its operator norm is bounded by $n C_{\Bogov}(n,\mia) \vol(\Omega)^{-1} \vol_{}(B_{\diam(\Omega)}(0)) \diam(\Omega)$. 
Moreover, $\supp \Bogov_{\mia} u \subseteq \overline\Omega$,
that is, the reconstructed potential has support contained within $\overline\Omega$. 
\\

\color{blue}
\subsection{Rewriting the potentials operators}

More properties of these operators become apparent after a change of variables. 
We write down the full definition of these operators and perform two substitutions.
For the Poincar\'e operator, we substitute $a = x + t(y-x)$, and then we substitute $s = (t-1)/t$,
leading to 
\begin{align*}
    \Poinc_{\mia} u(x) 
    &= 
    \vol(\Omega)^{-1}
    \int_{\Omega} \int_{1}^\infty (t-1)^{\mia-1}t^{n-\mia} 
    \chi_{\Omega}\left(x+t(y-x)\right) 
    (x-y)\lrcorner u(y) \,dt\,dy 
    \\
    &=
    \vol(\Omega)^{-1}
    \int_{\bbR^{n}} \chi_{\Omega}(a) \,(x-a)\lrcorner \int_{0}^{1} t^{\mia-1} u\left(a+t(x-a)\right)\,dt\,da
    .
\end{align*}
For the Bogovski\u{\i} operator, we first substitute $a = y + t(x-y)$, and then we substitute $s = t/(t-1)$,
leading to 
\begin{align*}
    \Bogov_{\mia} u(x) 
    &= 
    \vol(\Omega)^{-1}
    \int_{\Omega} \int_{1}^\infty (t-1)^{n-\mia}t^{\mia-1} 
    \chi_{\Omega}\left(y+t(x-y)\right) 
    (x-y)\lrcorner u(y) \,dt\,dy 
    \\
    &=
    - 
    \vol(\Omega)^{-1}
    \int_{\bbR^{n}} \chi_{\Omega}(a) \,(x-a)\lrcorner \int_{1}^\infty t^{\mia-1} u\left(a+t(x-a)\right)\,dt\,da
    .
\end{align*}
% We first discuss the support properties of this operator. 
% Suppose that $u \in C^{\infty}\Alt^{\mia-1}(\bbR^n)$ satisfies $\supp u \subseteq \overline\Omega$.
% Then $\Bogov_{\mia} u(x) = 0$ whenever $x \notin \overline\Omega$,
% meaning $\supp \Bogov_{\mia} u \subseteq \overline\Omega$.
% 
Given $a \in \Omega$, we introduce the potentials 
\begin{align*}
    \Poinc_{\mia,a} u(x) 
    &:= 
    (x-a)\lrcorner \int_{0}^{1} t^{\mia-1} u\left(a+t(x-a)\right)\,dt
    ,
    \\
    \Bogov_{\mia,a} u(x) 
    &:= 
    - (x-a)\lrcorner \int_{1}^\infty t^{\mia-1} u\left(a+t(x-a)\right)\,dt
    .
\end{align*}
By definition,
\begin{align*}
    \Poinc_{\mia} u(x) 
    =
    \vol(\Omega)^{-1}
    \int_{\Omega} \Poinc_{\mia,a} u(x) \,da,
    \quad 
    \Bogov_{\mia} u(x) 
    =
    \vol(\Omega)^{-1}
    \int_{\Omega} \Bogov_{\mia,a} u(x) \,da
    .
\end{align*}
On the background of this rewriting, we can establish additional operator norm bounds for the operator norms. 
These do not depend on the eccentricity of the domain.

We begin with the Poincar\'e operator. 
By an application of Jensen's inequality, operator norm estimates, and substitutions, we find 
\begin{align*}
    \| \Poinc_{\mia} u \|_{L^{p}(\Omega)}^{p}
    &
    \leq 
    \diam(\Omega)^{p}
    \vol(\Omega)^{-1}
    \int_{0}^{1} \int_{\Omega} \int_{\Omega} 
    t^{p(k-1)} |u( a + t(x-a) )|^{p} \,dt \,da \,dx
    \\&
    = 
    \diam(\Omega)^{p}
    \int_{0}^{1} 
    \iint\limits_{\substack{ (z,a) \in \Omega \times \Omega \\ z \in (1-t) a + t \Omega } }
    \vol(t\Omega)^{-1}
    t^{p(k-1)} |u( z )|^{p} \,dz \,da \,dt
    \\&
    = 
    \diam(\Omega)^{p}
    \int_{0}^{1} 
    \iint\limits_{\substack{ (z,a) \in \Omega \times \Omega \\ a \in \frac{z}{1-t} + \frac{t}{1-t} \Omega } }
    \vol(t\Omega)^{-1}
    t^{p(k-1)} |u( z )|^{p} \,dz \,da \,dt
    \\&
    = 
    \diam(\Omega)^{p}
    \int_{\Omega} 
    |u( z )|^{p}
    \int_{0}^{1} 
    \vol\left(\left\{ 
        \Omega \cap ( \tfrac{1}{1-t} z + \tfrac{t}{1-t} \Omega )
    \right\}\right)
    \frac{ t^{p(k-1)} }{ \vol(t\Omega) }
    \,dt \,dz 
    .
\end{align*}
\color{red}
A comparable estimate follows for the Bogovski\u{\i} operator with the substitution 
\begin{align*}
    \| \Bogov_{\mia} u \|_{L^{p}(\Omega)}^{p}
    &
    \leq 
    \diam(\Omega)^{p}
    \vol(\Omega)^{-1}
    \int_{1}^{\infty} \int_{\Omega} \int_{\Omega} 
    t^{p(k-1)} |u( a + t(x-a) )|^{p} \,dt \,da \,dx
    \\&
    = 
    \diam(\Omega)^{p}
    \int_{1}^{\infty} 
    \iint\limits_{\substack{ (z,a) \in \Omega \times \Omega \\ z \in (1-t) a + t \Omega } }
    \vol(t\Omega)^{-1}
    t^{p(k-1)} |u( z )|^{p} \,dz \,da \,dt
    \\&
    = 
    \diam(\Omega)^{p}
    \int_{1}^{\infty} 
    \iint\limits_{\substack{ (z,a) \in \Omega \times \Omega \\ a \in \frac{z}{1-t} + \frac{t}{1-t} \Omega } }
    \vol(t\Omega)^{-1}
    t^{p(k-1)} |u( z )|^{p} \,dz \,da \,dt
    \\&
    = 
    \diam(\Omega)^{p}
    \int_{\Omega} 
    |u( z )|^{p}
    \int_{1}^{\infty} 
    \vol\left(\left\{ 
        \Omega \cap ( \tfrac{1}{1-t} z + \tfrac{t}{1-t} \Omega )
    \right\}\right)
    \frac{ t^{p(k-1)} }{ \vol(t\Omega) }
    \,dt \,dz 
    .
\end{align*}
\color{blue}
We estimate 
\begin{align*}
    \int_{0}^{1}
    \vol\left(\left\{ 
        \Omega \cap ( \tfrac{1}{1-t} z + \tfrac{t}{1-t} \Omega )
    \right\}\right)
    \frac{ t^{p(k-1)} }{ \vol(t\Omega) }
    \ dt
    &
    \leq 
    \int_{0}^{1}
    \min\left( 
        \vol\left(\Omega\right), 
        \vol\left( \tfrac{t}{1-t} \Omega \right) 
    \right)
    \frac{ t^{p(k-1)} }{ \vol(t\Omega) }
    \ dt
    \\&
    \leq 
    \int_{0}^{1}
    \min\left( \tfrac{1}{t^{n}}, \tfrac{1}{(1-t)^n} \right) 
    t^{p(k-1)} 
    \ dt
    \\&
    \leq 
    \int_{0}^{1}
    \min\left( \tfrac{1}{t^{n}}, \tfrac{1}{(1-t)^n} \right) 
    t^{k-1} 
    \ dt
    .
\end{align*}
The last integral is handled via the basic observations
\begin{align*}
    \int_{0}^{\frac 1 2} 
    \frac{ t^{k-1} }{ (1-t)^{n} }
    \ dt
    \leq 
    \int_{0}^{\frac 1 2} 
    (1-t)^{-n+k-1}
    \ dt
    =
    \int_{\frac 1 2}^{1} 
    t^{-n+k-1}
    \ dt
    =
    \begin{cases}
        \ln(2)                 & \text{$n=k$}
        \\
        \frac{2^{n-k}-1}{n-k} & \text{otherwise.}
    \end{cases}
\end{align*}

\subsection{Interaction of potentials with the exterior derivative}
\color{black}
We study the interaction of the Poincar\'e and Bogovski\u{\i} operators with the exterior derivative in more detail.
% 
The main arguments are well-known and establish the exactness of several de~Rham complexes. 
We recapitulate these arguments since our variants of the regularized potential operators are not yet included in the published literature.

@@

\clearpage
We now provide the desired bi-Lipschitz transformation:
on the one hand, the nonlinear reflection across the interface between the selected simplex and the remainder of the local star,
and on the other hand, the bi-Lipschitz contraction from the local star onto the complement of the selected simplex. 
We give detailed estimates for the singular values of their Jacobians.

>>>>

\begin{remark}\label{remark:fullrecursivesum}
    \color{red}
    We briefly outline how  to obtain an estimate for the Poincar\'e--Friedrichs constant from the recursive estimate in Theorem~\ref{theorem:poincarefriedrichsestimate:grad}.
    The potential $w$ for the gradient $\nabla u$ satisfies 
    \begin{align*}
        \| w \|_{L^{p}(T_{0})} \leq A_{0} \| \nabla u \|_{L^{p}(T_{0})},
        \qquad 
        % \| w \|_{L^{p}(T_{m})} \leq A_{m} \| \nabla u \|_{L^{p}(T_{m} \cup T_{m-1})}                             + B_{m} \| w \|_{L^{p}(T_{m-1})},
        \| w \|_{L^{p}(T_{m})} \leq A_{m} \| \nabla u \|_{L^{p}(T_{m})} + A'_{m} \| \nabla u \|_{L^{p}(T_{m-1})} + B_{m} \| w \|_{L^{p}(T_{m-1})},
    \end{align*}
    where $A_{m}, A'_{m}, B_{m} \geq 0$ are numbers and $T_{0}, T_{1}, \dots, T_{m-1}, T_{m}$ is a face path.
    Unwrapping the recursion for the norm over the $m$-th simplex, we get a total expression of the form 
    \begin{align}\label{math:fullrecursivesum}
        \| w \|_{L^{p}(T_{m})} 
        &
        \leq 
        \sum_{\ell=0}^{m}   \left( B_{m} \cdots B_{\ell+1} \right) A_{\ell} \| \nabla u \|_{L^{p}(T_{\ell})}
        +
        \sum_{\ell=0}^{m-1} \left( B_{m} \cdots B_{\ell+2} \right) A'_{\ell+1} \| \nabla u \|_{L^{p}(T_{\ell})}
        =:
        \sum_{\ell=0}^{M} C_{m,\ell} \| \nabla u \|_{L^{p}(T_{\ell})}
        .
    \end{align}
    Here, $C_{m,\ell}$ is the coefficient of $\| \nabla u \|_{L^{p}(T_{\ell})}$, possibly zero, as it appears in the unwrapped recursive estimate of $\| w \|_{L^{p}(T_{m})}$. 
    The global Poincar\'e--Friedrichs inequality follows via H\"older's inequality:
    \begin{align*}
        \| w \|_{L^{p}(\Omega)}^{p}
        &
        \leq 
        \sum_{m=0}^{M}
        \| w \|_{L^{p}(T_{m})}^{p}
        % \\&
        \leq 
        \sum_{m=0}^{M}
        \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac p q}
        \sum_{\ell=0}^{M} 
        \| \nabla u \|_{L^{p}(T_{\ell})}^{p} 
        \leq 
        \left(
            \sum_{m=0}^{M}
            \left( \sum_{\ell=0}^{M} C_{m,\ell}^{q} \right)^{\frac p q}
        \right)
        \| \nabla u \|_{L^{p}(\Omega)}^{p} 
        ,
    \end{align*}
    where $q \in [1,\infty]$ satisfies $1 = 1/p + 1/q$ and with obvious modifications if $p=1$ or $p=\infty$. 
    In other words, the Poincar\'e--Friedrichs inequality is estimated by first taking the $q$-norm of the coefficients in the full sum~\eqref{math:fullrecursivesum} and then taking $p$-norm of these intermediate sums.
\end{remark}

@@

We analyze the Bogovski\u{\i} potential operator by similar means. 
Suppose that $u \in L^{\infty}\Alt^{\mia}(\bbR^{n})$ with $\supp u \subseteq \overline\Omega$ and that $x \in \bbR^{n}$.
First, if $x \notin \Omega$, then the convexity of $\Omega$ implies that $y + t( x - y ) \notin \Omega$ for all $t > 1$. Hence, $\calG_{\mia}(x,y) = 0$ and therefore $\Bogov_{\mia} u(x) = 0$ in that case.
Consider now the case $x \in \overline\Omega$. 
We estimate $\Bogov_{\mia} u(x)$ pointwise by 
\begin{align*}
    \left| \Bogov_{\mia} u(x) \right|
    &=
    \left| 
        \int_{\Omega} \calG_{\mia}(x,y) \,(x-y)\lrcorner u(y)\,dy
    \right| 
    \\&\leq 
    \int_{\Omega} \vol(\Omega)^{-1} \sum_{\jeza=0}^{\mia-1}\tbinom{\mia-1}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} |x-y|^{\jeza+1-n} |u(y)| \,dy
    \\&\leq 
    \int_{\bbR^{n}} \vol(\Omega)^{-1} \sum_{\jeza=0}^{\mia-1}\tbinom{\mia-1}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} \chi_{B_{\diam(\Omega)}(0)}(x-y) |x-y|^{\jeza+1-n} |u(y)| \,dy
    .
\end{align*}
Using once more the radial integrals discussed above, we compute 
% We recall the radial integrals 
% \begin{align*}
%     \int_{B_{\diam(\Omega)}(0)} |z|^{\jeza+1-n} dz
%     =
%     \vol_{n-1}(S_1) \int_{0}^{\diam(\Omega)} r^{\jeza+1-n} r^{n-1} dr
%     =
%     \vol_{n-1}(S_1) \int_{0}^{\diam(\Omega)} r^{\jeza} dr
%     =
%     \vol_{n-1}(S_1) \frac{\diam(\Omega)^{\jeza+1}}{\jeza+1}
%     .
% \end{align*}
% We compute 
\begin{align*}
    &
    \int_{\bbR^{n}} \sum_{\jeza=0}^{\mia-1} \tbinom{\mia-1}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} \chi_{B_{\diam(\Omega)}(0)}(z) |z|^{\jeza+1-n} \,dz
    \\&
    =
    \sum_{\jeza=0}^{\mia-1} \tbinom{\mia-1}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} \int_{B_{\diam(\Omega)}(0)} |z|^{\jeza+1-n} \,dz
    \\&
    =
    \vol_{n-1}(S_1) \sum_{\jeza=0}^{\mia-1} \tbinom{\mia-1}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} \frac{\diam(\Omega)^{\jeza+1}}{\jeza+1}
    %\\&
    =
    \vol_{n-1}(S_1) \diam(\Omega)^{n+1} \underbrace{ \sum_{\jeza=0}^{\mia-1} \frac{ \tbinom{\mia-1}{\jeza} }{ (n-\jeza)(\jeza+1) } }_{ =: C_{\Bogov}(n,\mia) \leq 2^{\mia-1}}
    .
\end{align*}
% Here, $C_{\Bogov}(n,\mia)$ is a numerical constant that depends only on $n$ and $\mia$ and which is bounded by $2^{\mia-1}$. 
Here we introduce the numerical constant 
\begin{gather}\label{equation:A_Bogov}
    C_{\Bogov}(n,\mia) := \sum_{\jeza=0}^{\mia-1} \frac{ \tbinom{\mia-1}{\jeza} }{ (n-\jeza)(\jeza+1) }, 
\end{gather}
which depends only on $n$ and $\mia$ and which is bounded by $2^{\mia-1}$. 
Similar as above,
the integral $\Bogov_{\mia} u(x)$ is absolutely convergent for any choice of $x \in \bbR^{n}$
and its magnitude is pointwise dominated by the convolution of $|u|$ against an integrable function.
Young's convolution inequality now implies: 
\begin{align*}
    \| \Bogov_{\mia} u \|_{L^{p}(\Omega)}
    &
    \leq 
    \vol_{n-1}(S_1) C_{\Bogov}(n,\mia) \frac{ \diam(\Omega)^{n} }{\vol(\Omega)} 
    \diam(\Omega)
    \| u \|_{L^{p}(\Omega)}
    \\&
    \leq 
    n C_{\Bogov}(n,\mia) \frac{ \vol_{}(B_{\diam(\Omega)}(0)) }{\vol(\Omega)} 
    \diam(\Omega)
    \| u \|_{L^{p}(\Omega)}
    .
\end{align*}
We have assumed so far that $u$ is essentially bounded.
Since that space is dense in the Lebesgue spaces, a density argument yields: 
for any $1 \leq p \leq \infty$ we have a bounded linear operator 
\begin{gather*}
    \Bogov_{\mia} : L^{p}\Alt^{\mia}(\Omega) \rightarrow L^{p}\Alt^{\mia-1}(\bbR^n).
\end{gather*}
% Its operator norm is bounded by $n C_{\Bogov}(n,\mia) \vol(\Omega)^{-1} \vol_{}(B_{\diam(\Omega)}(0)) \diam(\Omega)$. 
Moreover, $\supp \Bogov_{\mia} u \subseteq \overline\Omega$,
that is, the reconstructed potential has support contained within $\overline\Omega$.

\subsection{Rewriting the potentials operators}

More properties of these operators become apparent after a change of variables. 
We write down the full definition of these operators and perform two substitutions.
For the Poincar\'e operator, we substitute $a = x + t(y-x)$, and then we substitute $s = (t-1)/t$,
leading to 
\begin{align*}
    \Poinc_{\mia} u(x) 
    &= 
    \vol(\Omega)^{-1}
    \int_{\Omega} \int_{1}^\infty (t-1)^{\mia-1}t^{n-\mia} 
    \chi_{\Omega}\left(x+t(y-x)\right) 
    (x-y)\lrcorner u(y) \,dt\,dy 
    \\
    &=
    \vol(\Omega)^{-1}
    \int_{\bbR^{n}} \chi_{\Omega}(a) \,(x-a)\lrcorner \int_{0}^{1} t^{\mia-1} u\left(a+t(x-a)\right)\,dt\,da
    .
\end{align*}
For the Bogovski\u{\i} operator, we first substitute $a = y + t(x-y)$, and then we substitute $s = t/(t-1)$,
leading to 
\begin{align*}
    \Bogov_{\mia} u(x) 
    &= 
    \vol(\Omega)^{-1}
    \int_{\Omega} \int_{1}^\infty (t-1)^{n-\mia}t^{\mia-1} 
    \chi_{\Omega}\left(y+t(x-y)\right) 
    (x-y)\lrcorner u(y) \,dt\,dy 
    \\
    &=
    - 
    \vol(\Omega)^{-1}
    \int_{\bbR^{n}} \chi_{\Omega}(a) \,(x-a)\lrcorner \int_{1}^\infty t^{\mia-1} u\left(a+t(x-a)\right)\,dt\,da
    .
\end{align*}
% We first discuss the support properties of this operator. 
% Suppose that $u \in C^{\infty}\Alt^{\mia-1}(\bbR^n)$ satisfies $\supp u \subseteq \overline\Omega$.
% Then $\Bogov_{\mia} u(x) = 0$ whenever $x \notin \overline\Omega$,
% meaning $\supp \Bogov_{\mia} u \subseteq \overline\Omega$.
% 
Given $a \in \Omega$, we introduce the potentials 
\begin{align*}
    \Poinc_{\mia,a} u(x) 
    &:= 
    (x-a)\lrcorner \int_{0}^{1} t^{\mia-1} u\left(a+t(x-a)\right)\,dt
    ,
    \\
    \Bogov_{\mia,a} u(x) 
    &:= 
    - (x-a)\lrcorner \int_{1}^\infty t^{\mia-1} u\left(a+t(x-a)\right)\,dt
    .
\end{align*}
By definition,
\begin{align*}
    \Poinc_{\mia} u(x) 
    =
    \vol(\Omega)^{-1}
    \int_{\Omega} \Poinc_{\mia,a} u(x) \,da,
    \quad 
    \Bogov_{\mia} u(x) 
    =
    \vol(\Omega)^{-1}
    \int_{\Omega} \Bogov_{\mia,a} u(x) \,da
    .
\end{align*}

\subsection{Interaction of potentials with the exterior derivative}

We study the interaction of the Poincar\'e and Bogovski\u{\i} operators with the exterior derivative in more detail.
% 
The main arguments are well-known and establish the exactness of several de~Rham complexes. 
We recapitulate these arguments since our variants of the regularized potential operators are not yet included in the published literature.

@@

We now provide the desired bi-Lipschitz transformation:
on the one hand, the nonlinear reflection across the interface between the selected simplex and the remainder of the local star,
and on the other hand, the bi-Lipschitz contraction from the local star onto the complement of the selected simplex. 
We give detailed estimates for the singular values of their Jacobians.
